---
title: Final Plot Output
format: html
toc: true
editor: visual
---
```{r}
knitr::opts_chunk$set(message = FALSE)
```

```{r}

library(ggplot2)
library(readr)
library(ggpubr)

```

## Plotting predicted WP at 5 cm 

```{r}

predictedWP_5final <- readr::read_csv("~/Documents/NRSM_491/flux_model/Derived_Data/flux_data5_10.csv") |>
                      ggplot2::ggplot(aes(datetime, y = FX_5_kPa)) +
                                   geom_line() +
                                   geom_hline(yintercept = -1500, color = "red") +
                                   labs(
                                      x = "",
                                      y = "Predicted Water Potential (-kPa)"
                                      ) 

predictedWP_5final

```

## Plotting predicted WP at 10 cm 

```{r}

predictedWP_10final <- readr::read_csv("~/Documents/NRSM_491/flux_model/Derived_Data/flux_data5_10.csv") |>
                       ggplot2::ggplot(aes(datetime, y = FX_10_kPa)) +
                                   geom_line() +
                                   geom_hline(yintercept = -1500, color = "red") +
                                   labs(
                                      x = "",
                                      y = "Predicted Water Potential (-kPa)"
                                      ) 

predictedWP_10final

```

## Plotting predicted flux between 5 and 10 cm 

```{r}

flux5_10 <- readr::read_csv("~/Documents/NRSM_491/flux_model/Derived_Data/flux_data5_10.csv") |>
            ggplot2::ggplot() +
                        geom_line(aes(datetime, flux)) +
                        labs(
                          x = "",
                          y = "Flux [cm/d]" 
                          ) +
                        geom_hline(yintercept = 0, color = "red")

flux5_10

```

## Precipitation Hyetograph

##### Creating hyetograph plot for total daily precipitation from 2023-01-01 to 2023-12-30

##### code modified from Schramm (2022, July 15). @mpschramm: Combine a hydrograph and hyetograph in ggplot2.

##### Retrieved from https://michaelpaulschramm.com/posts/2022-07-15-hydrograph/ 

```{r}

precip_hyet <- readr::read_csv("~/Documents/NRSM_491/flux_model/Derived_Data/aceabsar_precip.csv") |>
               ggplot2::ggplot() +
                        geom_col(aes(
                                  datetime, 
                                  `Precipitation [cm]`, 
                                  fill = "Total Daily Precipitation [cm]")) +
                        scale_y_reverse(
                                    position = "left",
                                    limits = c(5, 0),
                                    breaks = 0:5,
                                    labels = 0:5,
                                    expand = c(0,0)) + 
                        scale_fill_manual(values = c("blue")) +
                        guides(fill = "none") +
                        labs(
                          y = "Total Daily Precipitation [cm]",
                          x = ""
                          )

precip_hyet

```

## Plotting final combo plot of flux with WP at 5 and 10 cm and total daily precipitation hyetograph

```{r, fig.height=10}

fluxcombo5_10 <- ggpubr::ggarrange(
                              precip_hyet,
                              flux5_10,
                              predictedWP_5final,
                              predictedWP_10final,
                              ncol = 1,
                              nrow = 4,
                              align = "v"
                              )

fluxcombo5_10

```
